19Q2

### 2019-06-03 19Q2.Rmd

# Edit direction column
g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity", NA))

@@

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
```

@@

```{r}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fuqs %>% count(Database, Drug, FusionPair, Fusion_Status)
```

@@

@@

```{r mut_wilcoxon_tests, eval=FALSE}
crispr <- unfactorize(crispr)
# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
crispr_filt <- filter(crispr, Gene %in% g2p_genes)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")

ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")

gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

```{r load_mut_wilcoxon_rds}
crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")

# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

@@

```{r load_fus_wilcoxon_rds}
ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
ctrp_signif_fus <- readRDS("./data_munging/rds/ctrp_signif_fusions.rds")
gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
```

@@

```{r fig.height=5, fig.width=10}
crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)

@@

ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ccle_fus_boxplot

@@

ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ctrp_fus_boxplot

@@

gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
gdsc_fus_boxplot
```

@@

@@

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  if(signif_grid_annot[i, j] == "O") {
                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
                  }
                }
                )
  return(ht)
}
```

>>>>

# Edit direction column
g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
g2p$Direction_Curated <- ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity|responsive")), "sensitivity", "none"))

@@

```{r}
cgi <- read.delim("./../../../Desktop/cgi_biomarkers_latest/cgi_biomarkers_per_variant.tsv", sep = "\t", header = TRUE)
```

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions_bcr_abl1 <- filter(fusions, X.FusionName %in% c("BCR--ABL1", "ABL1--BCR"))
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
```

@@

```{r}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
```

@@

ggpubr's convention for symbols indicating statistical significance:

- ns: p > 0.05
- *: p <= 0.05
- **: p <= 0.01
- ***: p <= 0.001
- ****: p <= 0.0001

@@

```{r mut_wilcoxon_tests, eval=FALSE}
# CRISPR
crispr <- unfactorize(crispr)
# crispr_signif_all_gene <- WilcoxonTestDF(dataframe = crispr, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g.rds")
crispr_filt <- filter(crispr, Gene %in% g2p_genes)
crispr_signif_gene <- WilcoxonTestDF(dataframe = crispr_filt, grouping = "Gene", outfile = "./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lineage <- WilcoxonTestDF(dataframe = crispr_filt, grouping = c("Gene", "disease"), outfile = "./data_munging/rds/crispr_signif_g2p_gl.rds")

# CCLE
ccle_filt <- filter(ccle, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ccle_filt$Gene <- factor(ccle_filt$Gene, ordered = FALSE)
ccle_filt <- unfactorize(ccle_filt)
ccle_signif_dg <- WilcoxonTestDF(dataframe = ccle, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ccle_signif_g2p_dg.rds")
ccle_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ccle_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ccle_signif_g2p_dgl.rds")

# CTRP
ctrp_filt <- filter(ctrp, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
ctrp_filt$Gene <- factor(ctrp_filt$Gene, ordered = FALSE)
ctrp_filt <- unfactorize(ctrp_filt)
# ctrp_signif_dg <- WilcoxonTestDF(dataframe = ctrp, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dg.rds")
ctrp_signif_g2p_dgl <- WilcoxonTestDF(dataframe = ctrp_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# GDSC
gdsc_filt <- filter(gdsc, Drug %in% g2p_drugs & Gene %in% g2p_dg_genes)
gdsc_filt$Gene <- factor(gdsc_filt$Gene, ordered = FALSE)
gdsc_filt <- unfactorize(gdsc_filt)
# gdsc_signif_dg <- WilcoxonTestDF(dataframe = gdsc, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "Drug_Gene"), g2p_list = unique(as.character(g2p_mut$Drug_Gene[!is.na(g2p_mut$Drug_Gene)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dg.rds")
gdsc_signif_g2p_dgl <- WilcoxonTestDF(dataframe = gdsc_filt, grouping = c("Drug", "Gene", "disease", "Drug_Gene_Lin"), g2p_list = unique(as.character(g2p_mut$Drug_Gene_Lin[!is.na(g2p_mut$Drug_Gene_Lin)])), outfile = "./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

```{r load_mut_wilcoxon_rds}
g2p_mut_4merge <- unique(select(g2p_mut, Drug_Gene, Direction_Curated))
g2p_mut_4merge$Direction_Numeric <- as.numeric(g2p_mut_4merge$Direction_Curated)

crispr_signif_g <- readRDS("./data_munging/rds/crispr_signif_g.rds")
crispr_signif_g2p_g <- readRDS("./data_munging/rds/crispr_signif_g2p_g.rds")
crispr_signif_lin <- readRDS("./data_munging/rds/crispr_signif_g2p_gl.rds")

ccle_signif_dg <- readRDS("./data_munging/rds/ccle_signif_dg.rds")
ccle_signif_g2p_dg <- readRDS("./data_munging/rds/ccle_signif_g2p_dg.rds")
# ccle_signif_g2p_dg <- merge(ccle_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
# ccle_signif_g2p_dg$Direction_Numeric <- ifelse(is.na(ccle_signif_g2p_dg$Direction_Numeric), 4, as.numeric(ccle_signif_g2p_dg$Direction_Numeric))
ccle_signif_dgl <- readRDS("./data_munging/rds/ccle_signif_g2p_dgl.rds")

# ctrp_signif_g <- readRDS("./data_munging/rds/ctrp_signif_dg.rds")
ctrp_signif_g2p_dg <- readRDS("./data_munging/rds/ctrp_signif_g2p_dg.rds")
# ctrp_signif_g2p_dg <- merge(ctrp_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
ctrp_signif_dgl <- readRDS("./data_munging/rds/ctrp_signif_g2p_dgl.rds")

# gdsc_signif_g <- readRDS("./data_munging/rds/gdsc_signif_dg.rds")
gdsc_signif_g2p_dg <- readRDS("./data_munging/rds/gdsc_signif_g2p_dg.rds")
# gdsc_signif_g2p_dg <- merge(gdsc_signif_g2p_dg, g2p_mut_4merge, by = "Drug_Gene", all.x = TRUE)
gdsc_signif_dgl <- readRDS("./data_munging/rds/gdsc_signif_g2p_dgl.rds")
```

@@

```{r load_fus_wilcoxon_rds}
g2p_fus_4merge <- unique(select(g2p_fus, Drug_FusionPair, Direction_Curated))

ccle_signif_fus <- readRDS("./data_munging/rds/ccle_signif_fusions.rds")
# ccle_signif_fus <- merge(ccle_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)

ctrp_signif_fus <- readRDS("./data_munging/rds/ctrp_signif_fusions.rds")
# ctrp_signif_fus <- merge(ctrp_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)

gdsc_signif_fus <- readRDS("./data_munging/rds/gdsc_signif_fusions.rds")
# gdsc_signif_fus <- merge(gdsc_signif_fus, g2p_fus_4merge, by = "Drug_FusionPair", all.x = TRUE)
```

@@

```{r crispr_mut_boxplots, fig.height=5, fig.width=10}
crispr_filt <- filter(crispr, Gene %in% g2p_mut_genes)
crispr_filt$Gene <- factor(crispr_filt$Gene, levels = g2p_mut_genes)
crispr_filt$Mutation <- as.character(crispr_filt$Mutation)
crispr_signif_filt <- filter(crispr_signif_g2p_g, Gene %in% g2p_mut_genes)
crispr_signif_filt$Gene <- factor(crispr_signif_filt$Gene, levels = g2p_mut_genes)

@@

ccle_fus_boxplot <- ggplot(data = ccle_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "springgreen4", "No" = "palegreen3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ccle_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ccle_fus_boxplot
# ggsave("./plots/manuscript/ccle_fus_boxplots.png", ccle_fus_boxplot, width = 8, height = 5, units = "in")

@@

ctrp_fus_boxplot <- ggplot(data = ctrp_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "steelblue4", "No" = "slategray3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = ctrp_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
ctrp_fus_boxplot
# ggsave("./plots/manuscript/ctrp_fus_boxplots.png", ctrp_fus_boxplot, width = 19, height = 5, units = "in")

@@

gdsc_fus_boxplot <- ggplot(data = gdsc_fus_filt) +
  facet_grid(FusionPair ~ Drug_f) +
  scale_color_manual(name = "Fusion Status", values = c("Yes" = "turquoise4", "No" = "paleturquoise3")) +
  geom_jitter(aes(x = Fusion_Status, y = Score, color = Fusion_Status), width = 0.2, alpha = 0.5, size = 0.6) +
  geom_boxplot(aes(x = Fusion_Status, y = Score), fill = "transparent", outlier.shape = NA, lwd = 0.3) +
  coord_cartesian(ylim = c(0, 1.2)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.2), labels = seq(0, 1, by = 0.2)) +
  geom_text(data = gdsc_signif_fus_filt, aes(x = 1.5, y = 1.1, label = p.signif)) +
  theme(legend.position = "top", legend.direction = "horizontal", axis.text.x = element_text(angle = 45, hjust = 0.8, vjust = 1)) +
  guides(color = guide_legend(override.aes = list(size = 3))) +
  labs(y = "AUC", x = "Fusion Status")
gdsc_fus_boxplot
# ggsave("./plots/manuscript/gdsc_fus_boxplots.png", gdsc_fus_boxplot, width = 12, height = 5, units = "in")
```

@@

```{r wilcoxon_heatmap_function_EDIT, eval=FALSE}
MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, legend_breaks, row_title_txt, radius) {
  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid < -log10(0.05)] <- NA

    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    # signif_grid_annot[signif_grid_annot == "No"] <- ""
    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p_log10", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid < -log10(0.05)] <- NA

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "Direction_Curated", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    # signif_grid_annot[signif_grid_annot == "No"] <- ""
    # signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  if(signif_grid_annot[i, j] == "none") {
                    grid.circle(x = x, y = y, r = radius, gp = gpar(fill = "transparent", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "sensitivity") {
                    grid.polygon(x = c(0, 0.5, 1), y = c(0, 1, 0), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
                  }
                  if(signif_grid_annot[i, j] == "resistance") {
                    grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc", gp = gpar(fill = "transparent", col = "black"))
                  }
                }
                )
  return(ht)
}
```

@@

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(legend_breaks[1], legend_breaks[length(legend_breaks)]), c("gray97", color))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70", at = legend_breaks, labels = legend_breaks)
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  # grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  if(signif_grid_annot[i, j] == "O") {
                    grid.circle(x = x - width*0.20, y = y - height*0.20, r = radius, default.units = "npc", gp = gpar(fill = "white", col = "black"))
                  }
                }
                )
  return(ht)
}
```

```{r testing, eval=FALSE}
grid.newpage()
grid.polygon(x = c(0.1, 0.1, 0.9, 0.9), y = c(0.1, 0.9, 0.9, 0.1), default.units = "npc",
             gp = gpar(), draw = TRUE, vp = NULL)
